### 2021-02-17 background.tex
second revision result,backgroud,setup. threats first version
first general review

Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} at a malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

@@

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system. Flowdroid~\cite{arzt:pldi-2014} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis. Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.

>>>>

Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

@@

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system. Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.

%Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.

### 2021-02-17 conclusionfutureworks.tex
first general review

Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities. Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including Boa et al. But the impact of static analysis on these mining approaches is unexplored currently. New static analysis techniques, like taint analysis algorithms can also support test generator tools to construct sandboxes.  \kn{The following sentence is completely not understandable. Consider splitting it. }However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of Bao et al. work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that ignoring the Joker tool \kn{Briefly mention what is joker tool prior to using the word}, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

>>>>

Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities. Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including \blls. But the impact of static analysis on these mining approaches is unexplored currently. The use of static analysis techniques, like taint analysis algorithms, to detect malicious behaviours, seems promising and can leverage sandboxes accuracy. However, many authors argue in favor of dynamic analysis for  mining sandboxes, highlight limitations at static analysis at this task, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

### 2021-02-17 introduction.tex
first general review

Our goal is to understand how static analysis
algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
first, we conduct a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}. Our study differs from the original work in two aspects: (a)
by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
and (c) by evaluating the performance of DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} in its original settings. Considering the other dynamic analysis approaches, which are
general purpose test case tools for Android, DroidMate has been designed with the goal of mining Android sandboxes---eventhough it has not been tested adequatly
in the work of Bao et al~\cite{DBLP:conf/wcre/BaoLL18}. In the second study, we explore to what extent we can complement the dynamic analysis approach using
tainted analysis algorithms.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 describes all malware apps used in our experiment, presenting their characterization. Section 4 introduces the study setting of our research and Section 5 complements presenting some results, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

>>>>

Our goal is to understand how static analysis
algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
first, we conduct a non-exact replication of the work of \blls. Our study differs from the original work in three aspects: (a)
by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
and (c) we considering more execution time for each apps analysed at our replication. In the second study, we explore to what extent we can complement the dynamic analysis approach using tainted analysis algorithms, through Flowdroid \cite{DBLP:conf/pldi/ArztRFBBKTOM14} tool.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 introduces the study setting of our research and Section 4 complements presenting some results and discussion, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 5 and 6, summarizes the paper, presenting some threats, presenting the final conclusions, and discussing our ideas for future works.

### 2021-02-17 results.tex
first general review

Our first study performed a non-exact replication of Bao et al work.
%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms(WS) and without the support
of DroidFax static analysis algorithms(WOS). \kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
\kn{Is this really improvement? Is this not "contribution" of droidfax. Improvement happens when an earlier approach detected malware without support of droidfax. Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax to the results is significant in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance by 100\% (as expected).
Next we discuss the result of each individual test generation tool.

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (WS) & Exec. (WOS) & Improvement (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  DroidMate &  64 &  48 & 25.00 \\ 
  DroidBot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

\subsubsection*{Monkey} sandbox for the execution WS detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps). Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%). This difference might be due to the Monkey using strategy that incorporates randomness for test case generation. \rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec. (II). \rb{Considering only one run for each configuration, that is Exec. (I) and Exec. (II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}

\subsubsection*{DroidBot} in the first execution (Exec. WS) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%). Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps. Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps. However, in our second execution (Exec WOS), its performance decreased to 20.58 \%. \rb{Not sure if the following sentence is right.} Despite this reduction, it detected the largest number of malicious apps in the Exec. WOS.

@@

\subsubsection*{Humanoid} presented the worse performance, even though a previous
work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. (I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%). Since Bao et al. did not explored Humanoid in their study, we do not have a baseline for comparison. Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.

@@

The Venn-diagram of Figure~\ref{fig:venn-plot1}
summarizes how the tools can complement each other.
Note in the diagram that 47 malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 77 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools. Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox. Contrasting with the Bao et al. work~\cite{DBLP:conf/wcre/BaoLL18},
our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
Android sandboxes.

@@

Altogether, ignoring the \joke tool, our study reveals that from 51.04\% (Humanoid)
to 73.95\% (Monkey) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms. Besides that, in the first execution, none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%). According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. \rb{In what follows we present some characteristics of malwares that had not been detected by the sandboxes.}

\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool. I think Thales could work on this, since he has helped Handrick to dissect the malwares.}

@@

\begin{finding}
  The performance of FlowDroid to identify malicious behavior
  using our approach is superior than the performance of the
  mining sandbox approach supported by dynamic analysis only---without
  the DroidFax static analysis algorithms.
\end{finding}

Additionally, we investigate if we could benefit from combining
the results from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
Venn-diagram summarizing the results. So, when combining
the results from FlowDroid and DroidFax, we were able to detect
67 of the malicious apps (69.79\%), a performance compatible
to that we found as response to the first execution of the
test case generation tools---which also considers the DroidFax
static analysis algorithms. More interesting, from those 67
malicious apps identified, 33 pairs had been found by
both tools (FlowDroid and DroidFax), even though they follow
a completely different static analysis approach. Furthermore,
FlowDroid shows to bem more effective than DroidFax, detecting 25 malicious
apps that had not been detected by DroidFax (while DroidFax detected nine
malicious apps that had not been detected by FlowDroid).

>>>>

Our first study performed a non-exact replication of the \blls.
%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms(WS) and without the support
of DroidFax static analysis algorithms(WOS). 
%\kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }
The Impact column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
%\kn{Is this really improvement? Is this not "contribution" of droidfax. Improvement happens when an earlier approach detected malware without support of droidfax. Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
In the \blls, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax to the results is significant in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance by 100\% (as expected).
Next we discuss the result of each individual test generation tool.

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  DroidMate &  64 &  48 & 25.00 \\ 
  DroidBot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

\subsubsection*{Monkey} sandbox for the execution WS detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps). Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%). This difference might be due to the Monkey using strategy that incorporates randomness for test case generation. %\rb{I am not convinced that the other tools do not employ any randomness.} 
For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec. (II). %\rb{Considering only one run for each configuration, that is Exec. (I) and Exec. (II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}

\subsubsection*{DroidBot} in the first execution (Exec. WS) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%). Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps. Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps. However, in our second execution (Exec WOS), its performance decreased to 20.58 \%. %\rb{Not sure if the following sentence is right.} 
Despite this reduction, it detected the largest number of malicious apps in the Exec. WOS.

@@

\subsubsection*{Humanoid} presented the worse performance, even though a previous
work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. (I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%). Since \blls did not explored Humanoid in their study, we do not have a baseline for comparison. Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.

@@

The Venn-diagram of Figure~\ref{fig:venn-plot1}
summarizes how the tools can complement each other.
Note in the diagram that 47 malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 77 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools. Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox. Contrasting with the \blls,
our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
Android sandboxes.

@@

Altogether, ignoring the \joke tool, our study reveals that from 51.04\% (Humanoid)
to 73.95\% (Monkey) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms. Besides that, in the first execution, none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%). According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. In what follows we present some characteristics of malware that had not been detected by the sandboxes (app 81 and app 65).

The first listing refers to app 81, which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language. That modification, does not threaten the user's device, however it is a unwanted private app change, and can characterize as misappropriation app.

\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - App81,language=Java, basicstyle=\tiny,label={lst:app81}]

1:B <     const-string v3, "Swith To "
---
1:M >     const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
\end{lstlisting}

\begin{lstlisting}[caption=AndroidManifest.xml - App 65, language=Java, basicstyle=\tiny,label={lst:app65}]

1:B <         <meta-data android:name="ADMOB_PUBLISHER_ID"
                     android:value="a14cf7346295891"/>
---
1:M >         <meta-data android:name="ADMOB_PUBLISHER_ID"
                     android:value="a14f099bfbf3c61"/>
\end{lstlisting}

The second listing refers to app 65. Your malicious version change the Android Manifest file, modifying the identification of meta-data ADMOB\_PUBLISHER\_ID. AdMob \cite{admob} is a mobile app monetization service, provided by Google. The Publisher ID \cite{publisherID} is the unique identifier for the AdMob account, and may be used to authenticate communication with Google. With that change, the malware is changing the ad revenue destination.

Now we present an malicious app that was detected by 2 sandboxes. The app 47 belongs to ours dataset, and is a troubling example. First it modify the Android Manifest file, adding permissions to receive and send SMS (Listing 3). Then, the malicious app use those permissions to performs MainService.java file, that get user's sensitive information, like International Mobile Equipment Identity (IMEI), and sink by SMS message (Listing 4). This malicious behaviours was detected by Droidbot and Humanoid tools.

\begin{lstlisting}[caption= AndroidManifest.xml - App 47, language=Java, basicstyle=\tiny,label={lst:app47:androidmanifest}]

67:M >    <uses-permission android:name="android.permission.RECEIVE_SMS"/>
68:M >    <uses-permission android:name="android.permission.SEND_SMS"/>
\end{lstlisting}

\begin{lstlisting}[caption= com/android/main/MainService.java - App 47, language=Java, basicstyle=\tiny,label={lst:app47:mainservice}]

492:M > localObject2 = (TelephonyManager)getSystemService("phone");
493:M > if (localObject2 != null)
494:M > {
495:M >  this.imei = ((TelephonyManager)localObject2).getDeviceId();
496:M >  this.imsi = ((TelephonyManager)localObject2).getSubscriberId();
497:M >  this.iccid = ((TelephonyManager)localObject2).getSimSerialNumber();
498:M > }
// [...]
519:M > if ("".equals(this.destMobile)) {
520:M >  getDestMobile();
521:M > }
522:M > sendSMS(this.destMobile, "imei:" + this.imei)
\end{lstlisting}

%\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool. I think Thales could work on this, since he has helped Handrick to dissect the malwares.}

@@

\begin{finding}
  The performance of FlowDroid to identify malicious behavior
  is superior than the performance of the
  mining sandbox approach supported by dynamic analysis only---without
  the DroidFax static analysis algorithms.
\end{finding}

Additionally, we investigate if we could benefit from combining
the results from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
Venn-diagram summarizing the results. So, when combining
the results from FlowDroid and DroidFax, we were able to detect
67 of the malicious apps (69.79\%), a performance compatible
to that we found as response to the first execution of the
test case generation tools---which also considers the DroidFax
static analysis algorithms. More interesting, from those 67
malicious apps identified, 33 pairs had been found by
both tools (FlowDroid and DroidFax), even though they follow
a completely different static analysis approach. Furthermore,
FlowDroid shows to be more effective than DroidFax, detecting 25 malicious
apps that had not been detected by DroidFax (while DroidFax detected nine
malicious apps that had not been detected by FlowDroid).

### 2021-02-17 setup.tex
first general review

Bao et al.'s ~\cite{DBLP:conf/wcre/BaoLL18} study explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis. Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results. Thus, this section present the settings of our study, whose goal is to perform this non-exact replication, and thus build a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.

@@

We conducted two studies to answer the research questions above. First we performed a non-exact replication of the \blls. Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.

The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

@@

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joker) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joker,
for $3$ minutes. We then investigate the performance of each tool to detect
malicious behaviors in the sandbox modeled by the test generation tool
under analysis.

%% Figure \ref{fig:setup} shows this experimental setup.

%% \begin{figure}[ht]
%%   \includegraphics[width=0.45\textwidth]{images/setup.png}
%%   \label{Experiment setup}
%%   \caption{}
%%   \label{fig:setup}
%% \end{figure}

>>>>

\blls explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis. Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results. Thus, this section present the settings of our study, whose goal is to perform this non-exact replication, and thus build a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.

@@

We conducted two studies to answer the research questions above. First we performed a non-exact replication of the \blls. Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded $6$ pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.

The others $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at \blls. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}. It is part of the Android SDK, and does not require any additional installation effort. Since Monkey was developed for stress testing, and can not perform text input, only generating
UI events, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

@@

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joker) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joker,
for $3$ minutes. We then investigate the performance of each tool to detect
malicious behaviors in the sandbox modeled by the test generation tool
under analysis. Figure \ref{fig:setup} shows this experimental setup.

\begin{figure}[ht]
   \includegraphics[width=0.45\textwidth]{images/setup2.png}
   \label{Experiment setup}
   \caption{Experiment setup}
   \label{fig:setup}
 \end{figure}

### 2021-02-17 threats.tex
first general review

Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution. To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions. So, the comparison between the results of this experiment and the experiment presented by Bao et al. could be more precise.
Beyond that, we tested only 96 of the original 102 pairs of apps in this experiment because the benchmark could not execute those six pairs of apps due to crashes in the Android emulator. This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.

>>>>

As any empirical work, this work also has limitations and threats to its validity.

\textbf{Internal Validity.} Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution. To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions. So, the comparison between the results of this experiment and the experiment presented by Bao et al. could be more precise. Beyond that, we tested only 96 of the original 102 pairs of apps in this experiment because the benchmark could not execute those six pairs of apps due to crashes in the Android emulator. This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.

\textbf{External Validity.} As this is a replication study, it brings some of the same threats \blls had presented. This study used the same set of apps, which were from a piggy-backed app dataset released by Li et al.~\cite{li2017understanding} So, using this dataset, we could not cover all categories of Android malware. Besides that, we only used a small number of test case generation tools in this study. To mitigate these threats and enrich our research data, we plan to test more apps and use other test case generation tools.

In this study, we used a single tool for Tainted Analysis. With such a small number of tools, we could not have a sample of what a static analysis tool could help in Tainted Analysis. So, we plan to use more tools to mitigate this threat.
